---
title: "Sample Cross-Sectional Meta-analysis"
author: "Lexi Strasburg"
date: "9/25/2022"
output: html_document
---

This example code was developed using the psychmeta tutorial from Dahlke & Wiernik (https://cran.r-project.org/web/packages/psychmeta/vignettes/overview.html). Includes example for WFC-Overall Engagement psychometric meta-analysis with example data, test of one moderator, and sensitvity analyses.

## Install & Load Packages
```{r}
#install.packages("here")
#install.packages("psychmeta")
#install.packages("metafor")
#install.packages("readr")
#install.packages("dplyr")
#install.packages("kableExtra")
```

```{r}
library(here)
library(psychmeta)
library(metafor)
library(readr)
library(dplyr)
library(kableExtra)
```

# Read in Data
```{r}
wfc.ee_meta = read_csv(here("Data", "Sample Data.csv"), show_col_types = FALSE)
```

# Select Columns
```{r}
wfc.ee_meta <- select(wfc.ee_meta, c(Study_Number, Short_Citation, N, Relationship_Filter, Ryy_Predictor,	Ryy_Criterion, Rxy, EE_Scale))
```

```{r echo=FALSE}
wfc.ee_meta %>% 
  dplyr::select(Study_Number, Short_Citation, N, Relationship_Filter, Ryy_Predictor,	Ryy_Criterion, Rxy) %>%
  knitr::kable() %>%
    kableExtra::kable_styling(full_width = FALSE) %>%
  scroll_box(width = "700px", height = "200px")
```

Filter for WFC - OE
```{r}
WFOE <- wfc.ee_meta %>%
  filter(Relationship_Filter == "work.to.family_overall.engagement")
```

# Run Psychometric Meta-Analysis
```{r}
meta_model1 <- ma_r(ma_method = "ad", 
                    rxyi = Rxy, 
                    n = N, 
                    rxx = Ryy_Predictor, 
                    ryy = Ryy_Criterion,
                    correct_rr_x = TRUE, 
                    correct_rr_y = TRUE,
                    sample_id = Study_Number, 
                    data = WFOE)
```

```{r}
meta_model1$meta_tables$`analysis_id: 1`$artifact_distribution[1]
```

## Moderator: Employee Engagement Scale
```{r}
meta_model2 <- ma_r(ma_method = "ad", 
                    rxyi = Rxy, 
                    n = N, 
                    rxx = Ryy_Predictor, 
                    ryy = Ryy_Criterion,
                    correct_rr_x = TRUE, 
                    correct_rr_y = TRUE,
                    moderators = EE_Scale,
                    sample_id = Study_Number, 
                    data = wfc.ee_meta)
```

```{r}
summary(meta_model2)
```

## Sensitivity Analyses
```{r}
ma_obj <- sensitivity(meta_model1,
                      leave1out = TRUE,
                      cumulative = TRUE,
                      sort_method = "weight")
```

# Egger's Test
```{r}
meta.data.es <- escalc(measure = "COR",
                       ni = N,
                       ri = Rxy,
                       data = WFOE)
```

```{r}
res <- rma(yi = yi, vi = vi, data = meta.data.es) 
regtest(res)
```

# Funnel Plot
```{r}
ma_obj <- plot_funnel(ma_obj = ma_obj)
out_plots <- get_plots(ma_obj)
out_plots$funnel$`analysis id: 1`$barebones
```

# Cumulative Meta-Analysis
```{r}
out_cumulative <- get_cumulative(ma_obj)
out_cumulative$`analysis id: 1`$barebones
```

```{r}
out_plots <- get_plots(ma_obj)
out_plots$cumulative$`analysis id: 1`$barebones$plots
```

# Leave One Out
```{r}
out_leave1out <- get_leave1out(ma_obj)
out_leave1out$`analysis id: 1`$barebones
```

```{r}
out_plots <- get_plots(ma_obj)
out_plots$leave1out$`analysis id: 1`$barebones$plots
```
