---
title: "Sample CoTiMa"
author: "Lexi Strasburg"
date: "9/22/2022"
output: html_document
---
This code was developed using the CoTiMa user guide from Dormann & Homberg (https://cran.r-project.org/web/packages/CoTiMA/vignettes/CoTiMA_User_Guide.pdf). Includes example for WFC-EE CoTiMa with example data, test of one moderator, and sensitivity analyses.
Note: the ctmaInit & ctmaFit functions produce a lot of output. Brief notes regarding interpretation are provided under these sections.

## Install & Load Packages
```{r}
#install.packages("devtools")
#install.packages("CoTiMA")
#install.packages("openxlsx")
```

```{r}
library("devtools")
library("CoTiMA")
library("openxlsx")
```

Example Code for WFC & EE CoTiMa

## Load Sample Data & Correct for Measurement Error 
```{r}
#Study 1
empcov1 <- matrix(c(1.00, 0.45, 0.57, 0.18,
                    0.45, 1.00, 0.31, 0.66,
                    0.57, 0.31, 1.00, 0.40,
                    0.18, 0.66, 0.40, 1.00), nrow=4, ncol=4)
delta_t1 <- .5
alphas1 <- c(.87, .88, .80, .94)
empcov1 <- ctmaCorRel(empcov1, alphas1)
variableNames1 <- c("WFC1", "EE1", "WFC2", "EE2")
dimnames(empcov1) <- list(variableNames1, variableNames1)
sampleSize1 <- 40
eeScale1 <- c("Utrecht")
nationality1 <- c("USA")
per_fem1 <- .60
age1 <- 32.0
hours1 <- 38.8
source1 <- c("1. A. Author & B. Author (2022)")
moderator1 <- c(1, 1, .60, 32, 38.8)

#Study 2
empcov2 <- matrix(c(1.00, 0.43, 0.71, 0.37,
                    0.43, 1.00, 0.34, 0.69,
                    0.71, 0.34, 1.00, 0.50,
                    0.37, 0.69, 0.50, 1.00), nrow=4, ncol=4)
delta_t2 <- 10
alphas2 <- c(.91, .88, .95, .81)
empcov2 <- ctmaCorRel(empcov2, alphas2)
variableNames2 <- c("WFC1", "EE1", "WFC2", "EE2")
dimnames(empcov2) <- list(variableNames2, variableNames2)
sampleSize2 <- 102
eeScale2 <- c("Utrecht")
nationality2 <- c("CA")
per_fem2 <- .48
age2 <- 28.4
hours2 <- 39.1
source2 <- c("2. A. Author & B. Author (2019)")
moderator2 <- c(1, 2, .48, 28.4, 39.1)

#Study 3
empcov3 <- matrix(c(1.00, 0.38, 0.54, 0.34, 0.60, 0.28,
                      0.38, 1.00, 0.34, 0.68, 0.28, 0.68,
                      0.54, 0.34, 1.00, 0.47, 0.66, 0.39,
                      0.34, 0.68, 0.47, 1.00, 0.38, 0.72,
                      0.60, 0.28, 0.66, 0.38, 1.00, 0.38,
                      0.28, 0.68, 0.39, 0.72, 0.38, 1.00), nrow=6, ncol=6)
delta_t3 <- c(20,20)
alphas3 <- c(.70, .88, .90, .92, .91, .90)
empcov3 <- ctmaCorRel(empcov3, alphas3)
variableNames3 <- c("WFC1", "EE1", "WFC2", "EE2", "WFC3", "EE3")
dimnames(empcov3) <- list(variableNames3, variableNames3)
sampleSize3 <- 40
eeScale3 <- c("Saks")
nationality3 <- c("USA")
per_fem3 <- .55
age3 <- 37.8
hours3 <- 41.0
source3 <- c("3. A. Author (2018)")
moderator3 <- c(2, 1, .55, 37.8, 41.0)
```

## Compile Studies To List
```{r}
activeDirectory <- "C:/Users/lexic/OneDrive/Dissertation/Sample Meta-Analysis Code"
CoTiMAstudyList_3 <- ctmaPrep(selectedStudies=c(1, 2, 3),
                                  activeDirectory = activeDirectory,
                                  addElements = c("work-to-family conflict", "engagement"),
                                  moderatorLabels=c("EE Scale", "Nationality", "Percent Female", "Age", "Work Hours"),
                                  moderatorValues=list(c("1 = Utrecht",
                                                         "2 = Saks"), c("1 = US", "2 = Canada"), "continuous", "continuous", "continuous"))
```

# Create Excel Spreadsheet with Study Information
```{r}
openXL(CoTiMAstudyList_3$excelSheets)
saveWorkbook(CoTiMAstudyList_3$excelSheets, overwrite=TRUE,
file=paste0(activeDirectory, "myExcelSheet.xlsx") )
```

## Initial Fit of CTSEM Model to Each Study
```{r}
activeDirectory <- "C:/Users/lexic/OneDrive/Dissertation/Sample Meta-Analysis Code"
coresToUse = 1 

CoTiMAInitFit_3 <- ctmaInit(primaryStudies=CoTiMAstudyList_3,
                                n.latent = 2,
                                activeDirectory = activeDirectory,
                                scaleTime = 1/20,
                                finishsamples = 20000,
                                checkSingleStudyResults = FALSE)

summary(CoTiMAInitFit_3)
saveRDS(CoTiMAInitFit_3, paste0(activeDirectory, "CoTiMAInitFit_3.rds"))
```
Auto and cross effects are found in "Estimates" section. These will be combined in next step to provide meta-analytic estimates.

# Full CoTiMA (Work-to-Family Conflict & Engagement)
```{r}
CoTiMAFullFit_3 <- ctmaFit(ctmaInitFit = CoTiMAInitFit_3, 
                               coresToUse = coresToUse)
summary(CoTiMAFullFit_3)
```
Note: examine the Upper & Lower Level CIs for DRIFT V1toV2 (invariant) and DRIFT V1toV2 (invariant) to test hypotheses.

## Plot Full CoTiMa
```{r}
plot(ctmaFitList(CoTiMAFullFit_3),
     timeUnit="Days",
     timeRange=c(.5, 20, 1) )
```

## Heterogenity & Publication Bias
```{r}
CoTiMABiG_D_BO <- ctmaBiG(CoTiMAInitFit_3)
summary(CoTiMABiG_D_BO)
plot(CoTiMABiG_D_BO)
```

## Moderated Full CoTiMa (Single Continuous Moderator)
```{r}
CoTiMAMod5onFullFit_3 <- ctmaFit(ctmaInitFit = CoTiMAInitFit_3,
mod.number = 5,
mod.type = "cont",
mod.names = "Work Hours",
coresToUse = 1,
scaleMod = TRUE)
saveRDS(CoTiMAMod5onFullFit_3, file=paste0(activeDirectory,
"CoTiMAMod5onFullFit_3.rds"))
summary(CoTiMAMod5onFullFit_3)
```
Note: examine the Upper & Lower CIs to reveal significance of moderator.


